Revised Interoceptive Accuracy Scale (IAS-R)

### 2023-10-15 analysis/analysis.Rmd
minor

---
title: "PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity"
subtitle: "Analysis"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "Revised Interoceptive Accuracy Scale (IAS-R)"
subtitle: "Analysis"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

@@

### CFA
